Probability

### 2016-04-23 prob.tex
prob.tex \subsection{Quantum Probability Spaces} Add examples...

We now formalize a \emph{quantum probability space} as follows~\cite{BirkhoffVonNeumann1936,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}.
We first assume an ambient Hilbert space~$\Hilb$ and define the
set of events $\qevents$ as all \emph{projections} on~$\Hilb$.
Each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
induces a probability measure $\mu_{\psi}:\qevents\rightarrow[0,1]$
on the space of events defined for any event $E\in\qevents$ as follows\footnote{Recently, people extend the domain of $\mu_{\psi}$ to all operators~$\mathcal{A}$
on $\Hilb$ and consider $\mu_{\psi}:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
When an operator $A\in\mathcal{A}$ is Hermitian, $\mu_{\psi}\left(A\right)$
is the expectation value of $A$. We does not take this approach because
we want to focus only on probability. }: 
\begin{equation}
\mu_{\psi}(E)= \ip{\psi}{E\psi} \label{eq:Born}
\end{equation}
Similarly to the classical case, this probability measure must satisfy:
\begin{itemize}
\item $\mu(\mathbb{1})=1$, and 
\item for a collection of pairwise orthogonal $E_i$, we have
  $\mu(\sum_i E_i) = \sum_i \mu(E_i)$. 
\end{itemize}
\yutsung{There are three ways to charactize a quantum probability:
\begin{enumerate}
\item The above two conditions as Gleason did.
\item As a linear functional on a {*} algebra.
\item As induced by a state vector by the Born rule (\ref{eq:Born}).
\end{enumerate}
According to equation (37) in section 4 Quantum Probability in \cite{Maassen2010},
the equalivance between 1. and 2. only hold for $d\ge3$ because of
Gleason' theorem. Therefore, it seems hard to get insight for how
to handle Gleason's theorem by {*}-algebra formulism...

@@

In the remainder of the paper, we consider variations of quantum
probability spaces motivated by computation of numerical quantities in
a world with limited resources:
\begin{itemize}
\item Instead of the Hilbert space $\Hilb$ (constructed over the
  uncountable and uncomputable complex numbers $\mathbb{C}$), we will
  consider variants constructed over finite
  fields~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
\item Instead of real-valued probability measures producing results in
  the uncountable and uncomputable interval $[0,1]$, we will consider
  finite set-valued probablitity measures~\cite{Artstein1972,PuriRalescu1983}.
\end{itemize}
We will then ask if it is possible to construct variants of quantum
probability spaces under these conditions. The main question is
related to the definition of probability measures: is it possible to
still define a probability measure as a function that depends on a
single state? Specifically,
\begin{itemize}
\item given a state $\ket{\psi}$, is there a probability measure
  mapping events to probabilities that only depends on $\ket{\psi}$?
  In the conventional quantum probability space, the answer is yes by
  the Born rule~\cite{Born1984,Mermin2007} and the map is given by:
  $E \mapsto \ip{\psi}{E\psi}$.
\item given a probability measure $\mu$
  mapping each event $E$
  to a probability, is there a \emph{unique} state $\psi$
  such that $\mu(E)
  =
  \ip{\psi}{E\psi}$. In the conventional case, the answer is yes by
  Gleason's
  theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
\end{itemize}

@@

%%%
\subsection{HIlbert Space with Finite Set-Valued Probability Measure}

>>>>

We now formalize a \emph{quantum probability space} as follows~\cite{BirkhoffVonNeumann1936,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}.
We first assume an ambient Hilbert space~$\Hilb$ and define the
set of events $\qevents$ as all \emph{projections} on~$\Hilb$.
Each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
induces a probability measure $\mu_{\psi}:\qevents\rightarrow[0,1]$
on the space of events defined for any event $E\in\qevents$ as follows\footnote{Recently, people extend the domain of $\mu_{\psi}$ to all operators~$\mathcal{A}$
on $\Hilb$ and consider $\mu_{\psi}:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
When an operator $A\in\mathcal{A}$ is Hermitian, $\mu_{\psi}\left(A\right)$
is the expectation value of $A$. We does not take this approach because
we want to focus only on probability. }: 
\begin{equation}
\mu_{\psi}(E)= \ip{\psi}{E\psi} \label{eq:Born}
\end{equation}
We may verify our previous examples. When events are orthogonal and
commutative, they can be measured together and their probability is
additive: 
\[
\mu_{0}(\proj{0})+\mu_{0}(\proj{1})=\mu_{0}(\proj{+})+\mu_{0}(\proj{-})=1=\mu_{0}(\mathbb{1})\textrm{ .}
\]
On the other hand, $\proj{0}$ and $\proj{-}$ are non-commutative,
and their total probabilities are not a probability of an event
\begin{eqnarray*}
\mu_{0}(\proj{0})+\mu_{0}(\proj{-}) & = & \frac{3}{2}>1\textrm{ .}
\end{eqnarray*}
Similarly to the classical case, this probability measure must satisfy:
\begin{itemize}
\item $\mu(\mathbb{1})=1$, and 
\item for a collection of pairwise orthogonal $E_i$, we have
  $\mu(\sum_i E_i) = \sum_i \mu(E_i)$. 
\end{itemize}
\yutsung{There are three ways to charactize a quantum probability:
\begin{enumerate}
\item The above two conditions as Gleason did.
\item As a linear functional on a {*} algebra.
\item As induced by a state vector by the Born rule (\ref{eq:Born}).
\end{enumerate}
According to equation (37) in section 4 Quantum Probability in \cite{Maassen2010},
the equalivance between 1. and 2. only hold for $d\ge3$ because of
Gleason' theorem. Therefore, it seems hard to get insight for how
to handle Gleason's theorem by {*}-algebra formulism...

@@

In the remainder of the paper, we consider variations of quantum
probability spaces motivated by computation of numerical quantities in
a world with limited resources:
\begin{itemize}
\item Instead of the Hilbert space $\Hilb$ (constructed over the
  uncountable and uncomputable complex numbers $\mathbb{C}$), we will
  consider variants constructed over finite
  fields~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
\item Instead of real-valued probability measures producing results in
  the uncountable and uncomputable interval $[0,1]$, we will consider
  finite set-valued probablitity measures~\cite{Artstein1972,PuriRalescu1983}.
\end{itemize}
We will then ask if it is possible to construct variants of quantum
probability spaces under these conditions. The main question is
related to the definition of probability measures: is it possible to
still define a probability measure as a function that depends on a
single state? Specifically,
\begin{itemize}
\item given a state $\ket{\psi}$, is there a probability measure
  mapping events to probabilities that only depends on $\ket{\psi}$?
  In the conventional quantum probability space, the answer is yes by
  the Born rule~\cite{Born1984,Mermin2007} and the map is given by:
  $E \mapsto \ip{\psi}{E\psi}$.
\item given a probability measure $\mu$
  mapping each event $E$
  to a probability, is there a \emph{unique} state $\psi$
  such that $\mu(E)
  =
  \ip{\psi}{E\psi}$? In the conventional case, the answer is yes by
  Gleason's
  theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
\end{itemize}

@@

%%%
\subsection{Hilbert Space with Finite Set-Valued Probability Measure}
